Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
problem convention

\vspace{-1cm}
\enlargethispage{.5cm}

@@

\smallskip
\begin{enumerate}[$\quad\bullet$]
\item \textbf{any initial seed}, regardless of whether it is acyclic or not (see \cref{exm:typeConeCA,fig:clusterFans,fig:labelFacetDefiningInequalititiesCA1,fig:labelFacetDefiningInequalititiesCA2} for examples in types~$A_3$ and~$C_3$~cyclic). In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} only treats acyclic initial seeds.

@@

\smallskip
\item \textbf{any positive real valued parameters}, regardless of whether they are rational or not. In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} naturally applies to rational parameters and then requires to apply an approximation argument.
\end{enumerate}

\smallskip
\noindent
\enlargethispage{.3cm}
These advantages all follow from one essential feature of our reversed approach.
Namely, it enables to completely separate the algebraic aspects from the geometric aspects of the problem:
\begin{enumerate}[$\quad\bullet$]
\item On the \textbf{algebraic side}, we study the relations between the $\b{g}$-vectors of a finite type cluster algebra and we show that the mesh mutations minimally generate these relations.
For this, we use representation theory in the setting of~$2$-Calabi--Yau triangulated categories, and we adapt M.~Auslander's proof that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type~\cite{Auslander1984} (see \cref{sec:clusterCategories}).

\smallskip
\item On the \textbf{geometric side}, we use elementary manipulations to show that a fan whose type cone is simplicial is affinely equivalent to the normal fan of sections of a high dimensional positive orthant with well-chosen affine subspaces (see \cref{sec:typeCone}). We then observe that our algebraic result precisely states that all type cones of $\b{g}$-vector fans of cluster algebras are simplicial from which we derive all our geometric consequences (see \cref{sec:applications}).
\end{enumerate}

@@

\medskip
Besides revisiting the construction of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and extending it to any initial seed (acyclic or not) in any finite type cluster algebra (simply-laced or not), our reversed approach is also successful when applied to the $\b{g}$-vector fans of other families of generalizations of the associahedron.
In the present paper, we explore specifically two families of such generalizations:

\smallskip
\begin{enumerate}[$\quad\bullet$]
\item \textbf{Gentle associahedra} were constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle bound quivers.  These complexes encompass two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}. It was shown in~\cite{PaluPilaudPlamondon-nonkissing, BrustleDouvilleMousavandThomasYildirim} that the non-kissing complex of a gentle bound quiver provides a combinatorial model for the support $\tau$-tilting complex~\cite{AdachiIyamaReiten} of the associated gentle algebra. Even for finite non-kissing complexes, it turns out that the type cone of the non-kissing fan is not always simplicial (see \cref{exm:nonSimplicialTypeConeNKC}). We prove however that the type cone is always simplicial when the gentle bound quiver is brick (at least $2$ relations in any cycle) and $2$-acyclic (no oriented cycle of length~$2$). Moreover, we precisely describe the facet-defining inequalities of the type cone in terms of linear dependences of $\b{g}$-vectors involved in certain mesh relations. We thus automatically derive a construction similar to that of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} describing all polytopal realizations of the $\b{g}$-vector fans of these brick $2$-acyclic bound quivers as sections of a positive orthant by well-chosen affine spaces (see \cref{subsec:typeConeCA}). Again, this result mainly relies on finding which relations minimally generate the relations between the $\b{g}$-vectors in the non-kissing complex. We present both a purely combinatorial proof (see \cref{subsec:typeConeCA}) and a purely algebraic proof for (non-necessarily gentle) brick algebras making use of extriangulated categories (see \cref{sec:extricats}).
Our algebraic proof is based on an analogue of a result of M. Auslander~\cite{Auslander1984} relating to minimal generators of Grothendieck groups.
Along the way, we need to generalise, for extriangulated categories, several results from cluster-tilting theory on indices~\cite{DehyKeller} and on abelian quotients~\cite{BuanMarshReiten, KellerReiten} that were known for triangulated categories.
We note however, that our assumptions are not quite the expected ones.
This is related to the fact that the Grothendieck groups of cluster categories are badly behaved (\eg the Grothendieck group of a cluster category of type~$A_2$ is trivial).
So as to overcome this difficulty, we replace the triangulated structure of cluster categories by some relative extriangulated structure, before considering Grothendieck groups.
This explains why we consider projective objects rather than cluster-tilting objects for extriangulated categories.

\medskip
\item \textbf{Graph associahedra} were defined by M.~Carr and S.~Devadoss~\cite{CarrDevadoss} in connection to C.~De Concini and C.~Procesi's wonderful arrangements~\cite{DeConciniProcesi}. As illustrated in~\cref{fig:specialGraphAssociahedra}, the graph associahedra of certain special families of graphs coincide with well-known families of polytopes: complete graph associahedra are permutahedra, path associahedra are classical associahedra, cycle associahedra are cyclohedra, and star associahedra are stellohedra. The graph associahedra were extended to the \defn{nestohedra}, which are simple polytopes realizing the nested complex of arbitrary building sets~\cite{Postnikov, FeichtnerSturmfels}. Graph associahedra and nestohedra have been geometrically realized in different ways: by successive truncations of faces of the standard simplex~\cite{CarrDevadoss}, as Minkowski sums of faces of the standard simplex~\cite{Postnikov, FeichtnerSturmfels}, or from their normal fans by exhibiting explicit inequality descriptions~\cite{Devadoss, Zelevinsky}. All these realizations have the same normal fan, called nested fan. We study the type cones of these nested fans (see \cref{subsec:typeConeGA}): we describe describe their facet-defining inequalities in terms of certain specific pairs of neighboring tubings and count them for the specific families of graph associahedra described earlier. For instance the type cone of the permutahedron coincides with the classical submodular functions on~$2^{[n]}$, described by~$2^{n-2} \binom{n}{2}$ inequalities. In fact, we observe that the type cone of a graphical nested fan is never simplicial except in the case of the classical associahedron (when the graph is the path). Our results describe nevertheless all polytopal realizations of the graphical nested fans.
\end{enumerate}

\smallskip
\enlargethispage{.5cm}
Further families of generalizations of the associahedron certainly deserve to be studied with our type cone approach.
We are investigating in particular brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and quotientopes~\cite{Reading-latticeCongruences, Reading-CambrianLattices, PilaudSantos-quotientopes}.
In fact, as already mentioned, it seems sometimes easier to find all polytopal realizations of a fan (by describing its type cone in terms of certain specific pairs of adjacent maximal cones) than to identify one specific explicit realization.
This is clearly the case when the type cone is simplicial as illustrated by the results of this paper: we naturally obtained all polytopal realizations of the $\b{g}$-vector fans of cluster algebras from cyclic seeds and of gentle algebras whose polytopality was only established very recently~\cite{HohlwegPilaudStella, PaluPilaudPlamondon-nonkissing}.
We believe that this gives reasonable hope that the polytopality of further fans could in the future be established using our type cone approach.
Tempting candidates are quotientopes for hyperplane arrangements beyond type~$A$, which are particularly interesting since the coarsenings of a fan essentially correspond to the faces of its type cone (see \cref{subsec:facesTypeCone}).

\medskip
Last but not least, the type cone approach naturally opens many research questions.
First, it raised the fundamental problem of describing the minimal relations among $\b{g}$-vectors in $2$-Calabi--Yau and extriangulated categories that we treat in \cref{part:algebra}.
It is also motivates the study of relevant objects revealed by the type cone dictionary between geometry and algebra:

@@

\newpage
\part{Type cones of $\b{g}$-vector fans}
\label{part:geometry}

@@

\begin{definition}
\label{def:meshMutation}
%Consider a seed~$\seed = (\B, \cluster)$ and a cluster variable~$x \in \cluster$.
The mutation of a seed~$\seed = (\B, \cluster)$ in the direction of a cluster variable~$x \in \cluster$ is a \defn{mesh mutation} that \defn{starts} (resp.~\defn{ends}) at~$x$ if the entries~$b_{xy}$ for~$y \in \cluster$ are all non-negative (resp.~all non-positive).
A mesh mutation is \defn{initial} if it starts at a cluster variable of an initial seed.
\vincent{Problem here. In my examples, the condition is to end at an initial cluster variable.}
We denote by~$\meshes$ the set of all pairs~$\{x,x'\}$ where~$x$ and~$x'$ are two cluster variables of~$\principalClusterAlgebra$ which are exchangeable via a non-initial mesh mutation.
\end{definition}

@@

@@

%%%%

@@

\yann{Rappels sur les categories extriangulees}
%%%%
\subsection{Statement of preliminary results on extriangulated categories}
\label{sect::prelim on extricats}

@@

%%%%
\subsection{Proofs of preliminary results and of Theorem~\ref{theorem::extricats}}
\label{sect::proofs extricats}

@@

%%%%
\subsection{Application to certain categories}

%%
\subsubsection{$2$-Calabi--Yau triangulated categories}
\label{sect::2CYTriangulated}

@@

%%%%
\subsection{Examples}

%%
\subsubsection{Associative algebras}
\begin{example}[A gentle algebra]
 Consider the algebra~$\Lambda$ given the the path algebra of the quiver
 \[
  \begin{tikzcd}
   1 \arrow[r, "\alpha"] & 2\arrow[r, "\beta"] & 3\arrow[r, "\gamma"] & 4
  \end{tikzcd}
 \]
 modulo the relation~$\gamma\beta\alpha = 0$.  The Auslander--Reiten quiver of the extriangulated category~$K^{[-1, 0]}(\proj\Lambda)$ is depicted below.
 \[
 \hspace*{-1cm}
 {\tiny
  \begin{tikzcd}
    &&&& (0\to P_4)\arrow[ddr] && (P_2\to 0)\arrow[ddr] && \\
    && (0\to P_3)\arrow[dr] && (P_1\to 0)\arrow[dr] &&&& \\
    & (0\to P_2)\arrow[dr]\arrow[ur] && (P_1\to P_3)\arrow[uur]\arrow[ur]\arrow[dr] && (P_2\to P_4)\arrow[uur]\arrow[dr] && (P_3\to 0)\arrow[dr] & \\
    (0\to P_1) \arrow[ur] && (P_1\to P_2)\arrow[ur] && (P_2\to P_3)\arrow[ur]  && (P_3\to P_4)\arrow[ur] && (P_4\to 0)
  \end{tikzcd}
 }
 \]
 The Auslander--Reiten quiver of the module category is obtained by taking the quotient by the ideal generated by the shifted projective modules.
 \[
 \hspace*{-1cm}
 {\footnotesize
  \begin{tikzcd}
    &&&& \begin{matrix} 4\\3\\2 \end{matrix}\arrow[ddr] && \\
    && \begin{matrix} 3\\2\\1 \end{matrix}\arrow[dr] &&&& \\
    & \begin{matrix} 2\\1 \end{matrix}\arrow[dr]\arrow[ur] && \begin{matrix} 3\\2 \end{matrix}\arrow[uur]\arrow[dr] && \begin{matrix} 4\\3 \end{matrix}\arrow[dr] & \\
    \begin{matrix} 1 \end{matrix} \arrow[ur] && \begin{matrix} 2 \end{matrix}\arrow[ur] && \begin{matrix} 3 \end{matrix}\arrow[ur] && \begin{matrix}4 \end{matrix}
  \end{tikzcd}
 }
 \]
 The conditions of Theorem~\ref{theo::brick-algebra-condition} are satisfied.

@@

\addtocontents{toc}{\bigskip}
\bibliographystyle{alpha}
\bibliography{typeConeAssociahedra}
\label{sec:biblio}

>>>>

\vspace{-1cm}
\enlargethispage{.4cm}

@@

\smallskip
\begin{itemize}
\item \textbf{any initial seed}, regardless of whether it is acyclic or not (see \cref{exm:typeConeCA,fig:clusterFans,fig:labelFacetDefiningInequalititiesCA1,fig:labelFacetDefiningInequalititiesCA2} for examples in types~$A_3$ and~$C_3$~cyclic). In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} only treats acyclic initial seeds.

@@

\smallskip
\item \textbf{any positive real valued parameters}, regardless of whether they are rational or not. In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} naturally applies to rational parameters and then requires to apply an approximation argument.
\end{itemize}

\smallskip
\noindent
\enlargethispage{.3cm}
These advantages all follow from one essential feature of our reversed approach.
Namely, it enables to completely separate the algebraic aspects from the geometric aspects of the problem:
\begin{itemize}
\item On the \textbf{algebraic side}, we study the relations between the $\b{g}$-vectors of a finite type cluster algebra and we show that the mesh mutations minimally generate these relations.
For this, we use representation theory in the setting of~$2$-Calabi--Yau triangulated categories, and we adapt M.~Auslander's proof that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type~\cite{Auslander1984} (see \cref{sec:clusterCategories}).

\smallskip
\item On the \textbf{geometric side}, we use elementary manipulations to show that a fan whose type cone is simplicial is affinely equivalent to the normal fan of sections of a high dimensional positive orthant with well-chosen affine subspaces (see \cref{sec:typeCone}). We then observe that our algebraic result precisely states that all type cones of $\b{g}$-vector fans of cluster algebras are simplicial from which we derive all our geometric consequences (see \cref{sec:applications}).
\end{itemize}

@@

\medskip
Besides revisiting the construction of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and extending it to any initial seed (acyclic or not) in any finite type cluster algebra (simply-laced or not), our reversed approach is also successful when applied to the $\b{g}$-vector fans of other families of generalizations of the associahedron.
In the present paper, we explore specifically two families of such generalizations.

\textbf{Gentle associahedra} were constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle bound quivers.  These complexes encompass two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}. It was shown in~\cite{PaluPilaudPlamondon-nonkissing, BrustleDouvilleMousavandThomasYildirim} that the non-kissing complex of a gentle bound quiver provides a combinatorial model for the support $\tau$-tilting complex~\cite{AdachiIyamaReiten} of the associated gentle algebra. Even for finite non-kissing complexes, it turns out that the type cone of the non-kissing fan is not always simplicial (see \cref{exm:nonSimplicialTypeConeNKC}). We prove however that the type cone is always simplicial when the gentle bound quiver is brick (at least $2$ relations in any cycle) and $2$-acyclic (no oriented cycle of length~$2$). Moreover, we precisely describe the facet-defining inequalities of the type cone in terms of linear dependences of $\b{g}$-vectors involved in certain mesh relations. We thus automatically derive a construction similar to that of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} describing all polytopal realizations of the $\b{g}$-vector fans of these brick $2$-acyclic bound quivers as sections of a positive orthant by well-chosen affine spaces (see \cref{subsec:typeConeCA}). Again, this result mainly relies on finding which relations minimally generate the relations between the $\b{g}$-vectors in the non-kissing complex. We present both a purely combinatorial proof (see \cref{subsec:typeConeCA}) and a purely algebraic proof for (non-necessarily gentle) brick algebras making use of extriangulated categories (see \cref{sec:extricats}).
Our algebraic proof is based on an analogue of a result of M. Auslander~\cite{Auslander1984} relating to minimal generators of Grothendieck groups.
Along the way, we need to generalise, for extriangulated categories, several results from cluster-tilting theory on indices~\cite{DehyKeller} and on abelian quotients~\cite{BuanMarshReiten, KellerReiten} that were known for triangulated categories.
We note however, that our assumptions are not quite the expected ones.
This is related to the fact that the Grothendieck groups of cluster categories are badly behaved (\eg the Grothendieck group of a cluster category of type~$A_2$ is trivial).
So as to overcome this difficulty, we replace the triangulated structure of cluster categories by some relative extriangulated structure, before considering Grothendieck groups.
This explains why we consider projective objects rather than cluster-tilting objects for extriangulated categories.

\textbf{Graph associahedra} were defined by M.~Carr and S.~Devadoss~\cite{CarrDevadoss} in connection to C.~De Concini and C.~Procesi's wonderful arrangements~\cite{DeConciniProcesi}. As illustrated in~\cref{fig:specialGraphAssociahedra}, the graph associahedra of certain special families of graphs coincide with well-known families of polytopes: complete graph associahedra are permutahedra, path associahedra are classical associahedra, cycle associahedra are cyclohedra, and star associahedra are stellohedra. The graph associahedra were extended to the \defn{nestohedra}, which are simple polytopes realizing the nested complex of arbitrary building sets~\cite{Postnikov, FeichtnerSturmfels}. Graph associahedra and nestohedra have been geometrically realized in different ways: by successive truncations of faces of the standard simplex~\cite{CarrDevadoss}, as Minkowski sums of faces of the standard simplex~\cite{Postnikov, FeichtnerSturmfels}, or from their normal fans by exhibiting explicit inequality descriptions~\cite{Devadoss, Zelevinsky}. All these realizations have the same normal fan, called nested fan. We study the type cones of these nested fans (see \cref{subsec:typeConeGA}): we describe describe their facet-defining inequalities in terms of certain specific pairs of neighboring tubings and count them for the specific families of graph associahedra described earlier. For instance the type cone of the permutahedron coincides with the classical submodular functions on~$2^{[n]}$, described by~$2^{n-2} \binom{n}{2}$ inequalities. In fact, we observe that the type cone of a graphical nested fan is never simplicial except in the case of the classical associahedron (when the graph is the path). Our results describe nevertheless all polytopal realizations of the graphical nested fans.

Further families of generalizations of the associahedron certainly deserve to be studied with our type cone approach.
We are investigating in particular brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and quotientopes~\cite{Reading-latticeCongruences, Reading-CambrianLattices, PilaudSantos-quotientopes}.
In fact, as already mentioned, it seems sometimes easier to find all polytopal realizations of a fan (by describing its type cone in terms of certain specific pairs of adjacent maximal cones) than to identify one specific explicit realization.
This is clearly the case when the type cone is simplicial as illustrated by the results of this paper: we naturally obtained all polytopal realizations of the $\b{g}$-vector fans of cluster algebras from cyclic seeds and of gentle algebras whose polytopality was only established very recently~\cite{HohlwegPilaudStella, PaluPilaudPlamondon-nonkissing}.
We believe that this gives reasonable hope that the polytopality of further fans could in the future be established using our type cone approach.
Tempting candidates are quotientopes for hyperplane arrangements beyond type~$A$, which are particularly interesting since the coarsenings of a fan essentially correspond to the faces of its type cone (see \cref{subsec:facesTypeCone}).

\medskip
\enlargethispage{.1cm}
Last but not least, the type cone approach naturally opens many research questions.
First, it raised the fundamental problem of describing the minimal relations among $\b{g}$-vectors in $2$-Calabi--Yau and extriangulated categories that we treat in \cref{part:algebra}.
It is also motivates the study of relevant objects revealed by the type cone dictionary between geometry and algebra:

@@

\newpage
\addtocontents{toc}{\vspace{-.2cm}}
\part{Type cones of $\b{g}$-vector fans}
\label{part:geometry}

@@

\begin{definition}
\label{def:meshMutation}
%Consider a seed~$\seed = (\B, \cluster)$ and a cluster variable~$x \in \cluster$.
The mutation of a seed~$\seed = (\B, \cluster)$ in the direction of a cluster variable~$x \in \cluster$ is a \defn{mesh mutation} that \defn{starts} (resp.~\defn{ends}) at~$x$ if the entries~$b_{xy}$ for~$y \in \cluster$ are all non-negative (resp.~all non-positive).
A mesh mutation is \defn{initial} if it ends at a cluster variable of an initial seed.
We denote by~$\meshes$ the set of all pairs~$\{x,x'\}$ where~$x$ and~$x'$ are two cluster variables of~$\principalClusterAlgebra$ which are exchangeable via a non-initial mesh mutation.
\end{definition}

@@

\vincent{Careful. There is a convention change with \cref{subsec:typeConeCA} and \cref{fig:labelFacetDefiningInequalititiesCA1,fig:labelFacetDefiningInequalititiesCA2}. Justify this change by the fact that we followed the convention of~\cite{BazierMatteDouvilleMousavandThomasYildirim} in \cref{subsec:typeConeCA}.}

@@

@@

\yann{Rappels sur les categories extriangulees}

\subsection{Statement of preliminary results on extriangulated categories}
\label{sect::prelim on extricats}

@@

\subsection{Recollections on extriangulated categories}

\subsection{Proofs of preliminary results and of Theorem~\ref{theorem::extricats}}
\label{sect::proofs extricats}

@@

\subsection{Application to certain categories}

\subsubsection{$2$-Calabi--Yau triangulated categories}
\label{sect::2CYTriangulated}

@@

\subsection{Examples}

%%

\subsubsection{Associative algebras}
\begin{example}[A gentle algebra]
 Consider the algebra~$\Lambda$ given the the path algebra of the quiver
 \[
  \begin{tikzcd}
   1 \arrow[r, "\alpha"] & 2\arrow[r, "\beta"] & 3\arrow[r, "\gamma"] & 4
  \end{tikzcd}
 \]
 modulo the relation~$\gamma\beta\alpha = 0$.  The Auslander--Reiten quiver of the extriangulated category~$K^{[-1, 0]}(\proj\Lambda)$ is depicted below.
 \[
 \hspace*{-1cm}
 {\tiny
  \begin{tikzcd}
    &&&& (0\to P_4)\arrow[ddr] && (P_2\to 0)\arrow[ddr] && \\
    && (0\to P_3)\arrow[dr] && (P_1\to 0)\arrow[dr] &&&& \\
    & (0\to P_2)\arrow[dr]\arrow[ur] && (P_1\to P_3)\arrow[uur]\arrow[ur]\arrow[dr] && (P_2\to P_4)\arrow[uur]\arrow[dr] && (P_3\to 0)\arrow[dr] & \\
    (0\to P_1) \arrow[ur] && (P_1\to P_2)\arrow[ur] && (P_2\to P_3)\arrow[ur]  && (P_3\to P_4)\arrow[ur] && (P_4\to 0)
  \end{tikzcd}
 }
 \]
 The Auslander--Reiten quiver of the module category is obtained by taking the quotient by the ideal generated by the shifted projective modules.
 \[
 \hspace*{-1cm}
 {\footnotesize
  \begin{tikzcd}
    &&&& \begin{matrix} 4\\3\\2 \end{matrix}\arrow[ddr] && \\
    && \begin{matrix} 3\\2\\1 \end{matrix}\arrow[dr] &&&& \\
    & \begin{matrix} 2\\1 \end{matrix}\arrow[dr]\arrow[ur] && \begin{matrix} 3\\2 \end{matrix}\arrow[uur]\arrow[dr] && \begin{matrix} 4\\3 \end{matrix}\arrow[dr] & \\
    \begin{matrix} 1 \end{matrix} \arrow[ur] && \begin{matrix} 2 \end{matrix}\arrow[ur] && \begin{matrix} 3 \end{matrix}\arrow[ur] && \begin{matrix}4 \end{matrix}
  \end{tikzcd}
 }
 \]
 The conditions of Theorem~\ref{theo::brick-algebra-condition} are satisfied.

@@

\addtocontents{toc}{\vspace{.2cm}}
\bibliographystyle{alpha}
\bibliography{typeConeAssociahedra}
\label{sec:biblio}
